Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-28 vesicle_code/docs/permeableVes/main.tex
yny

@@

At the beginning of the simulations a vesicle is initialized
above the center line $y=0$, and it migrates towards the center
line~\cite{dan-vla-mis2009}. For an impermeable vesicle, depending on
the vesicles reduced area and the flow rate, the equilibrium vesicle shape
is either an axisymmetric parachute or bullet, or an asymmetric
tank-treading slipper~\cite{kao-bir-mis2009}. 
%
%To validate our methods,
%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%for the steady state shape of an impermeable vesicle
%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%qualitatively agree, Kaoui et al.~report that the vesicles with
%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%are undergoing a tank treading motion, and we therefore report them as
%asymmetric slippers.
%
Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial reduced area is summarized in
Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
%
As observed for the planar shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the reduced area of the equilibrium vesicle shape in
Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper. We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow. The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}. RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
Here we investigate the role of membrane permeability to water when a cell is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
again to $16\mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
= 0.65$ that spans $10\mu$m of the total channel width and investigate
the effects of the permeability rate and the maximum flow velocity. We
color the vesicle according to the sign of its flux---fluid flows into
the vesicle in red regions and out of the vesicle in blue regions.

>>>>

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.45\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:schematics} A caption}
\end{figure}

@@

At the beginning of the simulations a semipermeable vesicle is initialized
above the center line $y=0$, and it migrates towards the center
line as in the impermeable case~\cite{dan-vla-mis2009}. However, for an impermeable vesicle, depending on
the initial reduced area and the maximum flow velocity $U$, the equilibrium vesicle shape
is either an axisymmetric parachute or bullet, or an asymmetric
tank-treading slipper~\cite{kao-bir-mis2009}. 
%
%To validate our methods,
%in Figure~\ref{fig:parabolicComposite}(a), we construct a phase diagram
%for the steady state shape of an impermeable vesicle
%vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
%qualitatively agree, Kaoui et al.~report that the vesicles with
%$\alpha=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
%axisymmetric. In our simulations these vesicles are slightly asymmetric,
%are undergoing a tank treading motion, and we therefore report them as
%asymmetric slippers.
%
Using several initial reduced areas and flow rates, we recreate the impermeable vesicle phase
diagram for vesicles with a permeability rate of $\beta = 10^{-3}$. The equilibrium vesicle shape for different $U$ and initial reduced area is summarized in
Figure~\ref{fig:parabolicComposite}(a). An example of a semi-permeable vesicle with $\alpha(0) = 0.9$ and $U=800$ $\mu m/s$ is
shown in Figure~\ref{fig:parabolicComposite}(c) and (d). 
%

As observed for the planar shear flow,
the steady state reduced area is independent of the initial reduced
area, and larger flow rates result in smaller steady state reduced
areas. We report the reduced area of the equilibrium vesicle shape in
Figure~\ref{fig:parabolicComposite}(a). At the smallest flow rate of $U= 200 \mu m/s$, the steady state reduced area is large, and the result
is an axisymmetric bullet. At the larger flow rates, the steady state
reduced area is smaller, and the result is an asymmetric tank-treading
slipper. We observe that the membrane permeability to water drastically alters the vesicle shape and position relative to the flow at equilibrium: At $\beta=10^{-3}$ the equilibrium vesicle depends only on the maximum velocity $U$ of the nonlinear shear flow. The higher $U$ the smaller the equilibrium reduced area and the further away vesicle is relative to the flow center at $y=0$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
Squeezing a cell or an elastic vesicle through a slit in microfluidics has gained popularity for its application in stress-induced release of macromolecules
\cite{ShareiEtAl2013_PNAS,Pak2015_PNAS,ZhangShenHoganBarakatMisbah2018_BJ,LuoBai2019_PoF}. RBCs go through submicron slits many times during their lifetime, and such process selects healthy, flexible RBCs to survive \cite{wu2015critical,LuPeng2019_PoF}.
Here we investigate the role of membrane permeability to water when a semi-permeable vesicle is squeezed through a contracting microfluidic channel similar to~\cite{wu2015critical},
where the width of the channel gradually decreases from $16\mu$m to $1.6\mu$m. The channel then immediately opens
again to $16\mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant maximum flow
rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
= 0.65$ that spans $10\mu$m of the total channel width and investigate
the effects of the membrane permeability to water and the maximum flow velocity on whether a vesicle can successfully pass through the slit. 
We color the vesicle according to the sign of its flux---red for influx and blue for efflux.
